\documentclass[12pt,letterpaper,oneside,roman]{moderncv}
%\usepackage[nenglish]{babel}              
\moderncvtheme[blue]{classic}                
\usepackage[latin1]{inputenc}
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths
%\usepackage{hyperref}
\setlength{\hintscolumnwidth}{5cm}

% personal data
\firstname{Simone}
\familyname{Aiola}
\title{\hbox{Curriculum Vitae et Studiorum}}                 % optional, remove the line if not wanted
\address{Department of Physics, Princeton University\\ 224 Jadwin Hall, Princeton NJ 08544\\}    % optional, remove the line if not wanted
\phone{+1-(609)-258-9622}                     % optional, remove the line if not wanted
\email{saiola@princeton.edu}         % optional, remove the line if not wanted
\homepage{homepage: put.webpage.here}
\quote{``Fatti non foste a viver come bruti, ma per seguir virtute e canoscenza''  \hbox{[Inferno - Dante Alighieri]}}

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%\AtBeginDocument{\settowidth{\hintscolumnwidth}{Birth date and place}}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\maketitle

\section{\textsc{Personal Information}}
\cvitem{Birth date and place}{June 4, 1988 - Rome, Italy}
\cvitem{Nationality}{Italian}
\cvitem{Languages}{Italian (native speaker), English (proficiency level)}

\section{\textsc{Research Interests}}
\cvitem{}{Cosmology: phenomenology and data analysis.}
\cvitem{}{Cosmic Microwave Background physics: temperature, polarization, lensing, Sunyaev-Zel'dovich effect.}
\cvitem{}{Cosmic Microwave Background analysis: map-making, simulations, time-ordered data analysis, n-point estimators.}

\section{\textsc{Research and Appointments}}
\cventry{Sept 2016 - present}{Postdoctoral Research Associate}{\small Supervisor: Jo Dunkley}{}{}{Princeton University - NJ}
\cventry{Aug 2013 - Aug 2016}{Graduate Student Researcher}{\small Advisor: Prof. Arthur Kosowsky}{}{}{University of Pittsburgh - PA, USA}
\cventry{Aug 2012 - Dec 2013}{Teaching Assistant}{}{University of Pittsburgh}{}{Courses: Lab for Physics and Engineers - Lab 0219 (Fall 2012), Intro to Physics 2 - Phys 0111 (Spring 2013 and Summer 2013), Stonehenge to Hubble - Astro 0088 (Fall 2013) - Stars, Galaxies and Cosmos - Astro 0089 (Summer 2014)}{}
\small{For official records of teaching performances please contact Leyla Hirschfeld, graduate program coordinator (lmh@pitt.edu).}

\section{\textsc{Education and Mentorship}}
\subsection{Education}
\cventry{Ph.D., Physics}{University of Pittsburgh, USA}{2012 - 2016}{}{}{}
\cvitem{}{Thesis: \emph{New Probes of Large-Scale CMB Anomalies}}
\cvitem{}{Advisor: Prof. Arthur Kosowsky}
\cventry{M.Sc., Physics}{University of Pittsburgh, USA}{2012 - 2013 (Awarded in 2014)}{}{}{}%arguments 3 to 6 are optional
\cventry{M.Sc., Astrophysics}{`La Sapienza' University of Rome, IT}{2010 - 2012}{}{}{} %arguments 3 to 6 are optional
\cvitem{}{Thesis: \emph{The Large-Scale Polarization Explorer: Optimization of the Observational Strategy}}
\cvitem{}{Advisors: Prof. Paolo de Bernardis and Dr. Francesco Piacentini}
\cvitem{}{Remarks: graduated \textit{cum laude}}
\cventry{B.Sc., Physics \& Astrophysics}{`La Sapienza' University of Rome, IT}{2007 - 2010}{}{}{} %arguments 3 to 6 are optional
\cvitem{}{Thesis: \emph{The Polarization of the Cosmic Microwave Background}}
\cvitem{}{Advisor: Prof. Paolo de Bernardis}
\subsection{Mentorship}
\cventry{Sept 2014 - Sept 2015}{Art and Sciences Teaching Assistant Mentor}{}{}{}{University of Pittsburgh - PA, USA}
\cventry{May 2014 - Aug 2016}{Undergraduate Mentorship}{}{Co-advising undergraduate student Ellis Herman (University of Richmond)}{}{Project: Probing the lack of large-scale CMB correlation with polarization and lensing measurements.}
\cventry{May 2013 - Aug 2016}{Undergraduate Mentorship}{}{Co-advising undergraduate student Bingjie Wang (University of Pittsburgh)}{}{Project: Large-scale anomalies in the CMB temperature sky.}

\section{\textsc{Awards and Fellowships}}
\cventry{2016}{McGill Astrophysics Postdoctoral Fellowship (declined)}{}{}{}{Department of Physics - McGill University}
\cventry{2014 and 2015}{Zaccheus Daniel Predoctoral Fellowship}{}{}{}{Department of Physics and Astronomy - University of Pittsburgh}
\cventry{2015}{Andrew Mellon Predoctoral Fellowship}{}{}{}{The Dietrich School of Art and Sciences - University of Pittsburgh}
\cventry{2014}{University of Pittsburgh School of Arts and Sciences Fellowship}{}{}{}{The Dietrich School of Art and Sciences - University of Pittsburgh}
\cventry{2014}{Nomination for Outstanding Teaching Assistant Awards}{}{}{}{American Association of Physics Teachers}
\cventry{2014}{Myron P. Garfunkel Excellence in Graduate Student Teaching Award 2014}{}{}{}{Department of Physics and Astronomy - University of Pittsburgh}

\section{\textsc{Collaborations}}
\cventry{May 2016 - Present}{Simons Observatory (SO)}{Main contributions: TOD-to-map working group, pipeline design working group.}{}{}{}
\cventry{Sept 2014 - Present}{Atacama Cosmology Telescope (ACT)}{Main contributions: Remote Control Observer, map-making working group, kSZ working group, cosmology from 2-point working group.}{}{}{}
\cventry{Sept 2010 - Aug 2012}{Large-Scale Polarization Explorer (LSPE)}{Main contributions: optimization of the scanning strategy for B-mode search.}{}{}{}

\section{\textsc{Computer skills and Competences}}
\cvitem{Languages}{Fortran, C/C++, IDL, Matlab (Octave), Python}
\cvitem{Cosmological tools}{CAMB, CLASS, polSPICE, HEALPix}
\cvitem{Supercomputing}{MPI, OpenMP, clusters used: SCINET and Hippo (South Africa)}

\section{\textsc{Talks and Poster Presentations}}
{\small For a detailed list of talks and posters with PDFs, visit my website. Below a list of talks from 2016.}\\
\newline
\cventry{July 2017}{`Maximum-likelihood map-making for ACT'}{}{contributed talk}{}{Advances in Theoretical Cosmology in Light of Data - Nordita, Stockholm}
\cventry{Feb 2017}{`Cosmology with ACT'}{}{contributed talk}{}{UKZN, SKA, and AIMS - South Africa}
\cventry{Feb 2017}{`Maximum-likelihood map-making for ACT'}{}{contributed talk}{}{Cosmology on Safari - South Africa}
\cventry{Mar 2016}{`New Probes of Large-scale CMB Anomalies'}{}{invited talk}{}{Astro Seminar - Case Wester Reserve University, USA}
%\cventry{Dec 2015}{`New Probes of Large-scale CMB Anomalies'}{}{contributed talk}{}{Cosmology Seminar - University of Oxford, UK}
%\cventry{Nov 2015}{`New Probes of Large-scale CMB Anomalies'}{}{contributed talk - invited}{}{Cosmology Seminar - SISSA (International School of Advanced Studies), Trieste, IT}
%\cventry{Nov 2015}{`New Probes of Large-scale CMB Anomalies'}{}{contributed talk - invited}{}{Astro Seminar - McGill University, CA}
%\cventry{July 2015}{`Microwave Background Correlations from Dipole Anisotropy Modulation'}{}{contributed talk}{}{Santa Fe Cosmology Workshop - St. John's College, Santa Fe, USA}
%\cventry{Feb 2015}{`Systematic Effects and Map-making with ACT'}{}{contributed talk}{}{ACT Collaboration Meeting - Princeton University, USA}
%\cventry{Nov 2014}{`Extreme-value Statistics for Testing Dark Energy'}{}{contributed talk}{}{Astro-statistics meeting - Carnegie Mellon University, USA}
%\cventry{Oct 2014}{`Extreme-value Statistics for Testing Dark Energy'}{}{contributed talk}{}{Physics Seminar - University of KwaZulu-Natal, ZA}
%\cventry{Sept 2014}{`A Constraint on the Dipole Modulation of the CMB'}{}{contributed talk}{}{Large-scale anomalies: from a priori to a posteriori - Center for Education and Research in Cosmology in Astrophysics, Case Wester Reserve University, USA}
%\cventry{May 2014}{`Extreme-value Statistics for Testing Dark Energy'*}{}{Poster}{}{Statistical Challenges in $21^{st}$ Century Cosmology - 306 IAU Symposium, Lisbon, PT}
%\cventry{April 2014}{`Extreme-value Statistics for Testing Dark Energy'}{}{contributed talk}{}{Neighborhood Workshop on Astrophysics and Cosmology - Penn State University, USA}
%\cventry{Dec 2013}{`$\Lambda$CDM Predictions on the Stacked Late-ISW signal'*}{}{contributed talk}{}{$27^{th}$ Texas Symposium - Dallas, USA}
%\cvitem{}{\small{*= Awarded Travel Grant}}
%\closesection{}                   % needed to renewcommands

\section{\textsc{References}}
\cventry{}{Prof. Arthur Kosowsky}{Ph.D. Advisor}{email: kosowsky@pitt.edu}{}{}
\cventry{}{Prof. Jo Dunkley}{Postdoc Supervisor}{email: jdunkley@princeton.edu}{}{}
\cventry{}{Prof. Lyman Page}{}{email: page@princeton.edu}{}{}
\subsection{Additional References}
\cventry{}{Prof. Glenn Starkman}{}{email: glenn.starkman@case.edu}{}{}
\cventry{}{Prof. Jonathan Sievers}{}{email: jonathan.sievers@gmail.com}{}{}
\section{}
\cvitem{}{\today}

\renewcommand{\listitemsymbol}{-} % change the symbol for lists

\end{document}