\documentclass[12pt,letterpaper,roman]{moderncv}
%\usepackage[nenglish]{babel}              
\moderncvtheme[blue]{classic}                
\usepackage[latin1]{inputenc}
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths
\usepackage{xpatch}
\xpatchcmd{\cventry}{\bfseries}{\mdseries}{}{}
\xpatchcmd{\cventry}{\bfseries}{\mdseries}{}{}
\setlength{\hintscolumnwidth}{4cm}

% personal data
\firstname{Simone}
\familyname{Aiola}
\title{\hbox{Publications}}                 % optional, remove the line if not wanted
\address{Department of Physics, Princeton University\\ 224 Jadwin Hall, Princeton NJ 08544\\}    % optional, remove the line if not wanted
\mobile{+1-(412)-251-6008}                     % optional, remove the line if not wanted
\email{saiola@princeton.edu}         % optional, remove the line if not wanted
\homepage{homepage: put.webpage.here}
%\extrainfo{Skype: cmbpol}                       %optional, remove the line if not wanted
%\extrainfo{LinkedIn: http://www.physicsandastronomy.pitt.edu/content/aiola-simone}
%\photo[80pt]{photo}                                   % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"The effort to understand the universe is one of the very few things that lifts human life a little above the level of farce, and gives it some of the grace of tragedy."  \hbox{"The First Three Minutes" - Steven Weinberg}} 
%\quote{``Fatti non foste a viver come bruti, ma per seguir virtute e canoscenza''  \hbox{[Inferno - Dante Alighieri]}}

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
\AtBeginDocument{\settowidth{\hintscolumnwidth}{Click for hyperlink:}}%
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\maketitle

\section{\textsc{Electronic Records}}
\cvitem{Click for hyperlink:}{{\href{https://scholar.google.com/citations?user=zl5L14QAAAAJ&hl=en}{Google Scholar}}, {\href{http://inspirehep.net/author/profile/S.Aiola.2} {inSPIRE}}, {\href{https://www.researchgate.net/profile/Simone_Aiola} {Research Gate}}, {\href{https://www.linkedin.com/pub/simone-aiola/35/156/38b}{LinkedIn}}}{}{}{}{}

\section{\textsc{Publications as Lead Author or with Substantial Contribution}}
\cventry{[1]}{Louis T., Grace E., Hasselfield M., Lungu M., Maurin L. et al. \textbf{(including Aiola S.)}}{}{\emph{The Atacama Cosmology Telescope: Two-Season ACTPol Spectra and Parameters}}{JCAP 95, 123529 (2017)}{arxiv:1610.02360}
\cventry{[2]}{De Bernardis F., \textbf{Aiola S.}, Vavagiakis E.M., Battaglia N., Niemack M.D. et al.}{}{\emph{Detection of the pairwise kinematic Sunyaev-Zel'dovich effect with BOSS DR11 and the Atacama Cosmology Telescope
}}{JCAP 1703, 03, 008 (2017)}{arxiv:1607.02139}
\cventry{[3]}{\textbf{Aiola S.}, Wang B., Kosowsky A., Kahniashvili T., Firouzjahi H.}{}{\emph{Microwave Background Correlations from Dipole Anisotropy Modulation}}{Phys.\ Rev.\ D 92, 063008 (2015)}{arxiv:1506.04405}
\cventry{[4]}{Yoho A., \textbf{Aiola S.}, Copi C., Kosowsky A., Starkman G.}{}{\emph{Using Polarization to Constrain the Lack of Large-Angle Correlation in CMB Temperature}}{Phys.\ Rev.\ D 91, 123504 (2015)}{arxiv:1503.05928}
\cventry{[5]}{\textbf{Aiola S.}, Kosowsky A., Wang B.}{}{\emph{Gaussian Approximation of Peak Values in the Integrated Sachs-Wolfe Effect}}{Phys.\ Rev.\ D 91, 043510 (2015)}{arxiv:1410.6138}

\section{\textsc{Publications as Member of Collaboration}}
\cventry{[6]}{Hilton M., Hasselfield M., Sifon C., Battaglia N. et al. \textbf{(including Aiola S.)}}{}{\emph{The Atacama Cosmology Telescope: The Two-Season ACTPol Sunyaev-Zel'dovich Effect Selected Cluster Catalog}}{(2017)}{arxiv:1709.05600}
\cventry{[7]}{Sherwin B., van Engelen A., Sehgal N., Madhavacheril M. et al. \textbf{(including Aiola S.)}}{}{\emph{The Atacama Cosmology Telescope: Two-Season ACTPol Lensing Power Spectrum}}{Phys.\ Rev.\ D 95, 123529 (2017)}{arxiv:1611.09753}
\cventry{[8]}{Thornton, R. J. et al. \textbf{(including Aiola S.)}}{}{\emph{The Atacama Cosmology Telescope: The polarization-sensitive ACTPol instrument}}{Astrophys.\ J.\ Suppl. 227, 2, 21 (2016)}{arxiv:1605.06569}
\cventry{[9]}{Schaan E., Ferraro S., Vargas-Maga\~ na M., Smith K., Ho S. et al. \textbf{(including Aiola S.)}}{}{\emph{Evidence for the kinematic Sunyaev-Ze\v{l}dovich effect with ACTPol and velocity
reconstruction from BOSS}}{Phys.\ Rev.\ D 93, 082002 (2016)}{arxiv:1510.06442}

\section{\textsc{Refereed Proceedings}}
\cventry{[10]}{\textbf{Aiola S.}, Kosowsky A., Wang B.}{}{\emph{Extreme-Value Statistics for Testing Dark Energy}}{Proceedings of the International Astronomical Union 10, 54-56 (2014)}{}
\cventry{[11]}{de Bernardis P., et al. \textbf{(including Aiola S.)}}{}{\emph{SWIPE: a bolometric polarimeter for the Large-Scale Polarization Explorer}}{Proc.\ SPIE Int.\ Soc.\ Opt.\ Eng. 8452 3F (2012)}{arxiv: 1208.0282}
\cventry{[12]}{LSPE Collaboration \textbf{(including Aiola S.)}}{}{\emph{The Large-Scale Polarization Explorer (LSPE)}}{Proc.\ SPIE 8446, Ground-based and Airborne Instrumentation for Astronomy IV, 84467A (2012)}{arxiv: 1208.0281}

\section{}
\cvitem{\today}{}
\end{document}